---
title: "Distribution Normal"
author: "Juan Reines"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
head(fastfood)
```

### Filter of McDonalds and Dairy Queen

```{r view-girls-counts}
mcdonalds <- fastfood %>%
  filter(restaurant == "Mcdonalds")

dairy_queen <- fastfood %>%
  filter(restaurant == "Dairy Queen")

```


### Graphic from Fat Calories

Plots for show distribution about calories fat from restaurants

```{r trend-girls}
mcmean <- mean(mcdonalds$cal_fat)
mcsd   <- sd(mcdonalds$cal_fat)
ggplot(data = mcdonalds, aes(x = cal_fat)) +
        geom_blank() +
        geom_histogram(aes(y = ..density..)) +
        stat_function(fun = dnorm, args = c(mean = mcmean, sd = mcsd), col = "tomato")
```


### Mean and Standard Desviation

Calculate the mean and standard desviation

```{r plot-prop-boys-arbuthnot}
dqmean <- mean(dairy_queen$cal_fat)
dqsd   <- sd(dairy_queen$cal_fat)
```


### Aproximate to Normal

Graphic for look near to Normal distribution

```{r dim-present}
ggplot(data = dairy_queen, aes(x = cal_fat)) +
        geom_blank() +
        geom_histogram(aes(y = ..density..)) +
        stat_function(fun = dnorm, args = c(mean = dqmean, sd = dqsd), col = "tomato")
```


### Graphic quartil-quartil

We can see the quartil-quartil from Dairy Queen

```{r count-compare}
ggplot(data = dairy_queen, aes(sample = cal_fat)) + 
  geom_line(stat = "qq")
```


### Near to Normal Distribution



```{r plot-prop-boys-present}
sim_norm <- rnorm(n = nrow(dairy_queen), mean = dqmean, sd = dqsd)
```


### Samples from Dairy Queen



```{r find-max-total}
qqnormsim(sample = cal_fat, data = dairy_queen)
```

